Object detection for Verification Based Annotation

### 2019-09-09 paper.tex
Updates from Overleaf

In this paper, we examine the properties of an object detector for Verification Based Annotation, where annotation is performed by having machine annotations checked and verified (and corrected, in this work) by a human annotator. We present our approach to object detection, where with a few modifications from standard practice, an object detector \cite{Lin2017} can be robust, without a large degree of parameter tweaking, for training object detection incrementally to annotate a wide variety of small-scale datasets with a variety of image resolution and object size.

>>>>

In this paper, we examine the properties of an object detector for Verification Based Annotation, where annotation is performed by having machine annotations checked and verified (and corrected, in this work) by a human annotator. We show that with a few modifications from standard practice, an object detector \cite{Lin2017} can be robust, without a large degree of parameter tweaking, for training object detection incrementally to annotate a wide variety of small-scale datasets with a variety of image resolution and object size.
